Sharing statistics for SPARQL Federation optimization, with emphasis on benchmark quality

### 2012-01-13 eswc-2012/phdsymp.tex
snip
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@85 43ef1190-90fd-4dd7-a769-d0121f02b80e

In this case, we must consider the possibility that the measurements
are impacted by random noise. Computer systems are generally very
deterministic systems, but there are nevertheless many such scenarios:
The underlying system may be doing other tasks. The garbage collection
of some languages may trigger at not easily foreseeable points. The
engine may use randomized algorithms, or the data may be of such a
nature that it triggers worst-case behaviour in situations the query
writer cannot foresee. All this contributes to that we should consider
the performance metric, whatever metric is used, as a \emph{stochastic
  variable}.

Doing this opens new methodological possibilities, first and foremost
using well-established statistical hypothesis testing rather than just
comparing averages.

@@

@@

@@

%\bibliographystyle{plain}
%\bibliographystyle{plain-csmin}
\bibliographystyle{splncs03}
\bibliography{selectivity,federation,benchmarks,optimization}

>>>>

In this case, we must consider the possibility that the measurements
are impacted by random noise. For example: The underlying system may
be doing other tasks. The garbage collection of some languages may
trigger at not easily foreseeable points. The engine may use
randomized algorithms, or the data may be of such a nature that it
triggers worst-case behaviour in situations the query writer cannot
foresee. All this contributes to that we should consider the
performance metric, whatever metric is used, as a \emph{stochastic
  variable}.

Doing this opens new methodological possibilities, first and foremost
using well-established statistical hypothesis testing or ranking
rather than just comparing averages.

@@

\paragraph{In SPARQL Federation}

@@

\paragraph{In Benchmarking}

@@

%\bibliographystyle{plain}
\bibliographystyle{plain-csmin}
%\bibliographystyle{splncs03}
\bibliography{selectivity,federation,benchmarks,optimization}
